Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/results_JCB.tex
results

To evaluate our method, we simulated with a random sequences from the MSA every time,
 $12$ times the $5-$fold, $10$ times the $10-$fold and $14$ times the $15-$fold coverage. And we 
 evaluated the ROC curve as in Sec.~\ref{sec:5S}.

@@

>>>>

To evaluate our method, we simulated with a random sequences from the MSA every time,
 $12$ times the $5-$fold, $10$ times the $10-$fold and $14$ times the $15-$fold coverage. And we 
 evaluated the ROC curve mostly as in Sec.~\ref{sec:5S}. In Fig.~\ref{fig:16s_all} they are computed
 over all positions, while in Fig.~\ref{fig:16s_bp} only over positions inside a base pair.

@@

Our data demonstrates that even on long sequences our algorithm shows interesting potential for 
error-correction applications. First, the AUC values (up to 0.81) when looking at all positions, 
in Fig.~\ref{fig:16s_all},  indicate that a signal has been successfully extracted. When restraining
to structured regions (i.e. base paired regions) we obtain AUC values up to 0.998.  Since 
contributions to the energy only comes from structured regions, this was an expected result.

An interesting feature is that best results are almost always when $\alpha=0$, i.e. all the contribution
comes from the isostericity. A notable exception is when the number of mutation is underestimated, 
in that case best performances were observed for non-nil values of $\alpha$.
